```{r}
# Read the data from the Excel file
library(readxl)
data <- read.csv("Data/Exp2/ResTrialLevel_Exp2.csv")
#print first 10 rows of the data
head(data, 10)
```

```{r}
group1 <- subset(data, Rep1 == 0)$Sharing
group2 <- subset(data, Rep1 == 1)$Sharing

# Perform the two-sample t-test
t.test(group1, group2, var.equal = TRUE)
```

```{r}
bartlett.test(Sharing ~ Rep1, data = data)
```


```{r}
result <- aov(Sharing ~ factor(Rep1), data = data)

# Print the ANOVA table
summary(result)
```
There is no significant difference in the mean sharing rating between participants who were exposed to a repeated statement and those who were not exposed to it.
We use one way ANOVA to test this hypothesis.

```{r}
# One way ANOVA on the mean sharing rating
#seaparate the data into two groups based on the repeated statement exposure
data1 <- data[data$Rep1 == 1,]
data2 <- data[data$Rep1 == 0,]

#perform one way ANOVA
oneway.test(Sharing ~ Rep1, data, var.equal = TRUE)
```


# hypothesis 2
```{r}
# conduct two-way ANOVA
# replacement has 0 rows, data has 6000
data_temp <- data

# convert to factor
data_temp$PercAccuracy <- as.factor(data_temp$PercAccuracy)
data_temp$Rep1 <- as.factor(data_temp$Rep1)
model <- aov(Sharing ~ PercAccuracy * Rep1, data = data_temp)

# model <- aov(SM ~ PercAccuracy * Rep1, data_temp)

# # display summary of results
summary(model)
print(model)
```

```{r}
# load necessary libraries
library(ggplot2)

# create scatter plot
ggplot(data_temp, aes(x=PercAccuracy, y=Sharing, color=factor(Rep1))) + 
  geom_point() +
  labs(x="Perceived Accuracy Rating", y="Sharing Rating", color="Repetition Status") +
  theme_dark()
```

# hypothesis 3
Correlation b/w percieved accuracy and sharing rating
```{r}
head(data,10)
cor.test(data$PercAccuracy, data$Sharing, method = "spearman")
```

```{r}
# library (tidyverse)
#import library for ggplot
library(ggplot2)
library(dplyr)

# Fit a linear regression model
avgData <- data.frame(data)
avgData <- avgData %>%
  group_by(ParticipantPublicID, True1, Rep1) %>%
  summarize(Sharing = mean(Sharing), 
            PercAccuracy = mean(PercAccuracy),
            SM = mean(SM))

head(avgData, 10)

# model <- lm(Sharing ~ PercAccuracy, data = data)

# # View the summary of the model
# summary(model)

# # Plot the data and the regression line
# ggplot(data, aes(x=PercAccuracy, y=Sharing)) + 
#   geom_point() +
#   geom_smooth(method = "lm", se = FALSE) +
#   labs(x="Perceived Accuracy Rating", y="Sharing Rating") +
#   theme_dark()
```

# Hypothesis 3


# Hypotheses 4
Mean sharing rating b/w participants who saw a trues statement and the ones who saw false statement
```{r}
#first we check if the variances are equal
bartlett.test(Sharing ~ True1, data = data)
```

```{r}
#separate groups based on the truth value of the statement
truth_data <- data[data$True1 == 1,]
false_data <- data[data$True1 == 0,]

#check if the variances are equal using F test
var.test(truth_data$Sharing, false_data$Sharing)
```

```{r}
t.test(truth_data$Sharing, false_data$Sharing, var.equal = FALSE)
```

# Hypothesis 5
Mean sharing rating b/w participants who were in sharing block first vs the accuracy block first

```{r}
library(readxl)
#read the xlsx file using readxl
data1 <- readxl::read_excel("Data/Exp2/ResultsIndivLevel_Exp2.xlsx")
#take only the columns titled ID1 and ShareFirst1
data1 <- data1[,c(1,9)]
head(data1, 10)
```

```{r}
#now in the original data, we separate them based on whether ShareFirst1 is 1 or 0 in data1 for each participant
#we then take the mean of the sharing rating for each group

merged_df <- merge(data, data1, by.x = "ParticipantPublicID", by.y = "ID1")
#rename the column named ShareFirst1...9 to ShareFirst
colnames(merged_df)[colnames(merged_df) == "ShareFirst1...9"] <- "ShareFirst"
head(merged_df, 10)
```

```{r}
share_first <- merged_df[merged_df$ShareFirst == 1,]
acc_first <- merged_df[merged_df$ShareFirst == 0,]
```

```{r}
head(share_first, 10)
```

```{r}
head(acc_first, 10)
```

```{r}
#check if the variances are equal using F test
var.test(share_first$Sharing, acc_first$Sharing)
```

```{r}
#perform t test
t.test(share_first$Sharing, acc_first$Sharing, var.equal = TRUE)
```